A Gaussian process model of human electrocorticographic data

### 2019-11-22 paper/main.tex
updated author list

\title{A Gaussian process model of human electrocorticographic data} 
\author{
  Lucy L. W. Owen$^{1}$,
  Andrew C. Heusser$^{1, 2}$, and
  Jeremy R. Manning$^{1\ast}$\\\\
$^{1}$Department of Psychological and Brain Sciences, Dartmouth College,\\
Hanover, NH 03755, USA\\
$^{2}$Akili Interactive,\\
Boston, MA 02110, USA}

>>>>

\title{A Gaussian process model of human electrocorticographic data} 
\author{
  Lucy L. W. Owen$^{1}$,
  Tudor A. Muntianu$^{1}$,
  Andrew C. Heusser$^{1, 2}$, \\
  Patrick Daly$^{3}$,
  Katherine Scangos$^{3}$, and
  Jeremy R. Manning$^{1\ast}$\\\\
$^{1}$Department of Psychological and Brain Sciences, Dartmouth College,\\
Hanover, NH 03755, USA\\
$^{2}$Akili Interactive,\\
Boston, MA 02110, USA\\
$^{3}$Weill Institute for Neurosciences, University of California, San Francisco,\\
San Francisco, CA 94121, USA}
